Discussion

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd

Our findings must be considered in light of several limitions.

>>>>

Our findings must be considered in light of several limitations.
First, it must be mentioned that a block design was used.
This allows for habituation effects of EMG activity within the block.
However, block designs are common in ER research [@Barreiros2019] and were used in previous studies [@Scheffel2019]. 
Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
It is also known that affect labeling might attenuate emotional experience [@Liebermann2007;@Torre2018]. 
That is why we decided not to have the ratings done after every image.
Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.
Taken together, these two facts may have led to slightly lower associations between SVs and predictors.

Third, it is a major limitation that participants had to use three given ER strategies.
